---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina =2 
)
```

gghazard : Improved Base and Grid Plots for Survival Hazard Cox Regression

The following functions are implemented:

The following data sets are included:

### News

- Version 0.0.0.9000 released

### Installation

```{r inst, eval=FALSE}
devtools::install_github("hrbrmstr/gghazard")
```

```{r opt, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r lib}
library(survival)
library(ggplot2)
library(gghazard)

# current verison
packageVersion("gghazard")

vfit <- coxph(Surv(time, status) ~ trt + factor(celltype) +
              karno + age, data=veteran, x=TRUE)
```

```{r, fig.width=9, fig.height=11}
gg_cox_zph(fortify(cox.zph(vfit)), pred_col="red")
```

```{r, fig.width=9, fig.height=11}
plot(cox.zph(vfit), smoothcol="red", confcol="red")
```

### Test Results

```{r}
library(gghazard)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
